slides for lab

### 2023-08-23 04. Analysis/scripts/04-01-reporting-presentation.Rmd
Update 04-01-reporting-presentation.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.width = 8,
                      fig.height = 4,
                      dpi = 300)
options(scipen=999)
tictoc::tic()
if(!("arsenal" %in% installed.packages()[,"Package"]))
{
  install.packages("arsenal")
}
if(!("beepr" %in% installed.packages()[,"Package"]))
{
  install.packages("beepr")
}
if(!("geomtextpath" %in% installed.packages()[,"Package"]))
{
  install.packages("geomtextpath")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
library(oesrrr)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(arsenal)
library(Hmisc)
library(readxl)
library(flextable)
library(ggthemes)
library(tidymodels)
library(patchwork)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.width = 8,
                      fig.height = 4,
                      dpi = 300)
options(scipen=999)
tictoc::tic()
if(!("arsenal" %in% installed.packages()[,"Package"]))
{
  install.packages("arsenal")
}
if(!("beepr" %in% installed.packages()[,"Package"]))
{
  install.packages("beepr")
}
if(!("geomtextpath" %in% installed.packages()[,"Package"]))
{
  install.packages("geomtextpath")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
install.packages("tigris")
library(oesrrr)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(arsenal)
library(Hmisc)
library(readxl)
library(flextable)
library(ggthemes)
library(tidymodels)
library(patchwork)
library(sf)
library(tigris)
options(tigris_class = "sf")
options(tigris_use_cache = TRUE)
```

@@

# Clusters and position categories

prep_d_02 <-
  d %>%
  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
         position_category_description = fct_infreq(position_category_description)) %>%
  group_by(position_category_description,.cluster_5) %>%
  count() %>%
  ungroup() %>%
  arrange(desc(n)) %>% 
  rename(num = n) %>% 
  mutate(
    position_category_description = fct_relevel(position_category_description, 
                                               "Offsite",
                                               "Onsite Flexible",
                                               "Onsite Required",
                                               "Other")
  )

prep_d_03 <- 
  prep_d_02 %>% 
  filter(position_category_description != "Other")

prep_d_04 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_05 <- 
  prep_d_03 %>% 
  full_join(prep_d_04) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  ) 
```

```{r}
p_1 <- 
  prep_d_05 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent of cluster in position category") +
  facet_wrap(facets = vars(position_category_description), nrow = 1) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

# Teleworkers, office visitors, and regions

```{r}
prep_d_01 <- 
  d %>% 
  group_by(gsa_region,.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(num = n)

prep_d_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_03 <- 
  prep_d_01 %>% 
  full_join(prep_d_02) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  ) %>% 
  mutate(
    gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
  )

prep_d_04 <- 
  prep_d_03 %>% 
  filter(.cluster_5 == "Teleworkers" |
           .cluster_5 == "Office\nvisitors"
           )
```

```{r}
p_1 <- 
  prep_d_04 %>% 
  ggplot(
    aes(x = gsa_region, y = n, fill = gsa_region)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent of cluster in region") +
  facet_wrap(facets = vars(.cluster_5), nrow = 1) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

# Hybrid, onsite, and disconnected workers and regions

```{r}
prep_d_01 <- 
  d %>% 
  group_by(gsa_region,.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(num = n)

prep_d_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_03 <- 
  prep_d_01 %>% 
  full_join(prep_d_02) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  ) %>% 
  mutate(
    gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
  )

prep_d_04 <- 
  prep_d_03 %>% 
  filter(.cluster_5 == "Hybrid\nworkers" |
           .cluster_5 == "Onsite\nworkers" |
           .cluster_5 == "Disconnected\nworkers")
```

```{r}
p_1 <- 
  prep_d_04 %>% 
  ggplot(
    aes(x = gsa_region, y = n, fill = gsa_region)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent of cluster in region") +
  facet_wrap(facets = vars(.cluster_5), nrow = 1) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

# States: MD, PA, and VA

```{r}
prep_d_01 <- 
  d %>% 
  group_by(location_state,.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(num = n)

prep_d_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_03 <- 
  prep_d_01 %>% 
  full_join(prep_d_02) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  )# %>% 
  # mutate(
  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
  # )

prep_d_04 <- 
  prep_d_03 %>% 
  filter(location_state %in% c("MD","PA","VA")
           )
```

```{r}
p_1 <- 
  prep_d_04 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent of cluster in state") +
  facet_wrap(facets = vars(location_state), nrow = 1) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

# States: CA and IL

```{r}
prep_d_01 <- 
  d %>% 
  group_by(location_state,.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(num = n)

prep_d_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_03 <- 
  prep_d_01 %>% 
  full_join(prep_d_02) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  )# %>% 
  # mutate(
  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
  # )

prep_d_04 <- 
  prep_d_03 %>% 
  filter(location_state %in% c("CA", "IL")
           )
```

```{r}
p_1 <- 
  prep_d_04 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent of cluster in state") +
  facet_wrap(facets = vars(location_state), nrow = 1) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

# District of Columbia

```{r}
prep_d_01 <- 
  d %>% 
  group_by(location_state,.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(num = n)

prep_d_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_03 <- 
  prep_d_01 %>% 
  full_join(prep_d_02) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  )# %>% 
  # mutate(
  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
  # )

prep_d_04 <- 
  prep_d_03 %>% 
  filter(location_state %in% c("DC")
           )
```

```{r}
p_1 <- 
  prep_d_04 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent of cluster in state") +
  facet_wrap(facets = vars(location_state), nrow = 1) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

# Clusters and staff offices

```{r}
prep_d_01 <- 
  d %>% 
  group_by(gsa_sso) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n))

prep_v_01 <- 
  prep_d_01 %>% 
  slice(2) %>% 
  pull(n)

prep_d_02 <-
  d %>%
  mutate(gsa_sso = fct_lump_min(gsa_sso, min = prep_v_01),
         gsa_sso = fct_infreq(gsa_sso)) %>%
  group_by(gsa_sso,.cluster_5) %>%
  count() %>%
  ungroup() %>%
  arrange(desc(n)) %>% 
  rename(num = n) %>% 
  mutate(gsa_sso = fct_relevel(gsa_sso,
                               "PBS",
                               "FAS",
                               "OCFO",
                               "Other"))

prep_d_03 <- 
  prep_d_02 %>% 
  filter(gsa_sso != "Other")

prep_d_04 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_05 <- 
  prep_d_03 %>% 
  full_join(prep_d_04) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  ) 
```

```{r}
p_1 <- 
  prep_d_05 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent of cluster in staff office") +
  facet_wrap(facets = vars(gsa_sso), nrow = 1) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 7))

# Clusters and series

```{r}
prep_d_01 <- 
  d %>% 
  group_by(occupational_series) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n))

prep_d_02 <-
  d %>%
  mutate(
    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
    occupational_series = fct_infreq(occupational_series)
  ) %>%
  group_by(occupational_series, .cluster_5) %>%
  count() %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  rename(num = n) %>%
  mutate(
    # occupational_series = fct_relevel(occupational_series,
    #                                   "1102",
    #                                   "1101",
    #                                   "0343",
    #                                   "Other"),
    occupational_series = recode(occupational_series,
                                 "1102" = "Contracting",
                                 "1101" = "General Business and Industry",
                                 "0343" = "Management and Program Analysis",
                                 "0501" = "Financial Administration and Program",
                                 "0560" = "Budget Analysis",
                                 "0301" = "Miscellaneous Administration and Program",
                                 "1170" = "Realty",
                                 "1176" = "Building Management",
                                 "2150" = "Transportation Operations",
                                 "2210" = "Information Technology Management"
                                 ),
    occupational_series = fct_relevel(
      occupational_series,
      "Budget Analysis",
      "Building Management",
      "Contracting",
      "Financial Administration and Program",
      "General Business and Industry",
      "Information Technology Management",
      "Management and Program Analysis",
      "Miscellaneous Administration and Program",
      "Realty",
      "Transportation Operations",
    )
  )

# prep_d_02
```

```{r}
prep_d_03 <-
  prep_d_02 %>%
  filter(
    occupational_series %in%
      c(
        # "Budget Analysis",
        # "Building Management",
        "Contracting",
        # "Financial Administration and Program",
        # "General Business and Industry",
        # "Information Technology Management",
        "Management and Program Analysis",
        "Miscellaneous Administration and Program"
        # "Realty",
        # "Transportation Operations"
      )
  )

prep_d_04 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_05 <- 
  prep_d_03 %>% 
  full_join(prep_d_04) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  ) %>% 
  mutate(
    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
  )
```

```{r}
p_1 <- 
  prep_d_05 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent of cluster in series") +
  facet_wrap(facets = vars(occupational_series), nrow = 1) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 7))

# Clusters and series

```{r}
prep_d_01 <- 
  d %>% 
  group_by(occupational_series) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n))

prep_d_02 <-
  d %>%
  mutate(
    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
    occupational_series = fct_infreq(occupational_series)
  ) %>%
  group_by(occupational_series, .cluster_5) %>%
  count() %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  rename(num = n) %>%
  mutate(
    # occupational_series = fct_relevel(occupational_series,
    #                                   "1102",
    #                                   "1101",
    #                                   "0343",
    #                                   "Other"),
    occupational_series = recode(occupational_series,
                                 "1102" = "Contracting",
                                 "1101" = "General Business and Industry",
                                 "0343" = "Management and Program Analysis",
                                 "0501" = "Financial Administration and Program",
                                 "0560" = "Budget Analysis",
                                 "0301" = "Miscellaneous Administration and Program",
                                 "1170" = "Realty",
                                 "1176" = "Building Management",
                                 "2150" = "Transportation Operations",
                                 "2210" = "Information Technology Management"
                                 ),
    occupational_series = fct_relevel(
      occupational_series,
      "Budget Analysis",
      "Building Management",
      "Contracting",
      "Financial Administration and Program",
      "General Business and Industry",
      "Information Technology Management",
      "Management and Program Analysis",
      "Miscellaneous Administration and Program",
      "Realty",
      "Transportation Operations",
    )
  )

# prep_d_02
```

```{r}
prep_d_03 <-
  prep_d_02 %>%
  filter(
    occupational_series %in%
      c(
        "Budget Analysis",
        # "Building Management",
        # "Contracting",
        "Financial Administration and Program",
        # "General Business and Industry",
        "Information Technology Management",
        # "Management and Program Analysis",
        # "Miscellaneous Administration and Program"
        # "Realty",
        # "Transportation Operations"
      )
  )

prep_d_04 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_05 <- 
  prep_d_03 %>% 
  full_join(prep_d_04) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  ) %>% 
  mutate(
    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
  )
```

```{r}
p_1 <- 
  prep_d_05 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent of cluster in series") +
  facet_wrap(facets = vars(occupational_series), nrow = 1) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 7))

# Clusters and series

```{r}
prep_d_01 <- 
  d %>% 
  group_by(occupational_series) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n))

prep_d_02 <-
  d %>%
  mutate(
    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
    occupational_series = fct_infreq(occupational_series)
  ) %>%
  group_by(occupational_series, .cluster_5) %>%
  count() %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  rename(num = n) %>%
  mutate(
    # occupational_series = fct_relevel(occupational_series,
    #                                   "1102",
    #                                   "1101",
    #                                   "0343",
    #                                   "Other"),
    occupational_series = recode(occupational_series,
                                 "1102" = "Contracting",
                                 "1101" = "General Business and Industry",
                                 "0343" = "Management and Program Analysis",
                                 "0501" = "Financial Administration and Program",
                                 "0560" = "Budget Analysis",
                                 "0301" = "Miscellaneous Administration and Program",
                                 "1170" = "Realty",
                                 "1176" = "Building Management",
                                 "2150" = "Transportation Operations",
                                 "2210" = "Information Technology Management"
                                 ),
    occupational_series = fct_relevel(
      occupational_series,
      "Budget Analysis",
      "Building Management",
      "Contracting",
      "Financial Administration and Program",
      "General Business and Industry",
      "Information Technology Management",
      "Management and Program Analysis",
      "Miscellaneous Administration and Program",
      "Realty",
      "Transportation Operations",
    )
  )

# prep_d_02
```

```{r}
prep_d_03 <-
  prep_d_02 %>%
  filter(
    occupational_series %in%
      c(
        # "Budget Analysis",
        "Building Management",
        # "Contracting",
        # "Financial Administration and Program",
        "General Business and Industry",
        # "Information Technology Management",
        # "Management and Program Analysis",
        # "Miscellaneous Administration and Program"
        "Realty",
        "Transportation Operations"
      )
  )

prep_d_04 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_05 <- 
  prep_d_03 %>% 
  full_join(prep_d_04) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  )  %>% 
  mutate(
    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
  )
```

```{r}
p_1 <- 
  prep_d_05 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent of cluster in series") +
  facet_wrap(facets = vars(occupational_series), nrow = 1) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 7))

# Clusters and series

```{r}
prep_d_01 <- 
  d %>% 
  group_by(occupational_series) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n))

prep_d_02 <-
  d %>%
  mutate(
    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
    occupational_series = fct_infreq(occupational_series)
  ) %>%
  group_by(occupational_series, .cluster_5) %>%
  count() %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  rename(num = n) %>%
  mutate(
    # occupational_series = fct_relevel(occupational_series,
    #                                   "1102",
    #                                   "1101",
    #                                   "0343",
    #                                   "Other"),
    occupational_series = recode(occupational_series,
                                 "1102" = "Contracting",
                                 "1101" = "General Business and Industry",
                                 "0343" = "Management and Program Analysis",
                                 "0501" = "Financial Administration and Program",
                                 "0560" = "Budget Analysis",
                                 "0301" = "Miscellaneous Administration and Program",
                                 "1170" = "Realty",
                                 "1176" = "Building Management",
                                 "2150" = "Transportation Operations",
                                 "2210" = "Information Technology Management"
                                 ),
    occupational_series = fct_relevel(
      occupational_series,
      "Budget Analysis",
      "Building Management",
      "Contracting",
      "Financial Administration and Program",
      "General Business and Industry",
      "Information Technology Management",
      "Management and Program Analysis",
      "Miscellaneous Administration and Program",
      "Realty",
      "Transportation Operations",
    )
  )

# prep_d_02
```

```{r}
prep_d_03 <-
  prep_d_02 %>%
  filter(
    occupational_series %in%
      c(
        # "Budget Analysis",
        "Building Management",
        # "Contracting",
        # "Financial Administration and Program",
        "General Business and Industry",
        # "Information Technology Management",
        # "Management and Program Analysis",
        # "Miscellaneous Administration and Program"
        "Realty",
        "Transportation Operations"
      )
  )

prep_d_04 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n)) %>% 
  rename(tot = n)

prep_d_05 <- 
  prep_d_03 %>% 
  full_join(prep_d_04) %>% 
  mutate(
    n = num/tot,
    text = scales::comma(num)
  )  %>% 
  mutate(
    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
  )
```

```{r}
p_1 <- 
  prep_d_05 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent of cluster in series") +
  facet_wrap(facets = vars(occupational_series), nrow = 1) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 7))

```{r}
# f <- file.path(params$google_drive_home,"03. Data Collection","tiger","tl_2022_us_state.zip")
# library(tigris)
# tigris::load_tiger(url = f)
```

# CONTINUE FROM HERE

```{r}
beepr::beep(sound = 5)
```

```{r}
